\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based TSDF Calculation

### 2024-03-07 Articles/IROS/root.tex
izbira primerov

\title{\LARGE \bf
Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based Robotic Manipulator Path Planning
}

@@

\begin{equation}
	C_d = A_d \odot K_d
	\label{eq:hadamard}
\end{equation}

@@

$\Delta i$, $\Delta j$ in $\Delta k$ predstavljajo število celic odmika od centralnega polja matrike, v katerem se nahaja naša točka na agentu v posamezno koordinatno smer.

@@

@@

@@

\section{INVERSE KINEMATICS}

\section{REPULSIVE VELOCITIES CALCULATION}

@@

>>>>

\title{\LARGE \bf
Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based TSDF Calculation
}

@@

%\begin{equation}
%	C_d = A_d \odot K_d
%	\label{eq:hadamard}
%\end{equation}

@@

$\Delta i = c_i - i$, $\Delta j = c_j - j$ in $\Delta k = c_k - k$ predstavljajo število celic odmika od centralnega polja matrike, v katerem se nahaja naša točka na agentu v posamezno koordinatno smer.

@@

\add{mogoče dodaj še kak stavek o izbiri dimenzij matrik}

@@

Another option is to use linearly falling weights.

\begin{equation}
	w_{\Delta j} =
	\begin{cases} 
		\frac{l - \Delta j }{l} & \text{if } \Delta j < 0 \text{~or }  \Delta j > 0 \\
		1 & \text{if } \Delta j = 0 \\
	\end{cases}
\end{equation}

@@

@@

\subsection{Repulsive Field Visualization}

\add{Visualization of the repulsive field around more or less complicated obstacles.}

\comment{}{we dont have the close obstacles bottlenecks}

\subsection{Manipulator Examples}

\add{EXAMPLE: MANIPULATOR AND COLUMN}

\add{EXAMPLE: MANIPULATOR AND MOVING NOISY BALL}

\subsection{Drone Example}

\add{EXAMPLE: DRONE MOVING THROUGH THE MAP OF OBSTACLES USING APF}
